Approximate Code: A Cost-Effective Erasure Coding Framework for Tiered Video Storage in Cloud Systems

### 2019-04-20 ApproximateCode.tex
Version 4! The draft

To address this problem, in this paper, we propose Approximate Code, which is an erasure coding framework for video applications in cloud storage systems. The key idea of Approximate Code is distinguishing the important data and unimportant data in videos with different capabilities of fault tolerance. On one hand, for important data, Approximate Code provides triple parities to provide high reliability. On the other hand, single/double parities are applied for unimportant data, which can save the storage cost and accelerate the recovery process. To demonstrate the effectiveness of Approximate Code, we conduct several experiments in Hadoop systems. The results show that, compared to traditional 3DFTs using various erasure codes such as RS, STAR and TIP-Code, Approximate Code reduces the number of parities by up to 60\%, saves the storage cost by up to 10\%, increase the recovery speed by up to 1.5X when single disk fails, and can reconstruct the whole video data via fuzzification when triple disks fail.
                                                                    q
\end{abstract}

@@

\section{Introduction}
For typical cloud storage systems such as Windows Azure \cite{calder2011windows} and Amazon AWS \cite{bermudez2013exploring}, erasure coding is a popular technique to provide both high reliability and low monetary cost \cite{EVENODD, RDP, BlaumRoth, XCode, CRS, TripleStar, TPtech, RSL}, where triple disk failure fault tolerant arrays (3DFTs) are widely used. Typical erasure codes can be divided into two categories, RS-based Codes \cite{RS} \cite{LRC} and XOR-based codes \cite{EVENODD, HCODE, STAR, tip}. RS-based codes are encoded according the Galois Field Computation in Reed Solomon Code \cite{RS}, which allow flexible configuration and have a little higher computation cost. XOR-based codes simplify the computation, but the scalability is a significant issue in previous literatures.

@@

To address the above problem, in this paper, we propose Approximate Code, which is an erasure coding framework to provide comprehensive solution for video data storage in cloud systems. The key idea of Approximate Code is treating the important/unimportant data in different ways. For important data, we add additional parities to provide high capability of fault tolerance. On the other hand, the unimportant data are encoded with a minimum number of parities, which only supply the basic requirement of the recovery. When triple disks fail, the lost data can be reconstructed via a fuzzy manner.

@@

\begin{table}[]
\caption{The symbols used in this paper.}\label{parameter}
\centering
\begin{tabular}{|c|l|}
\hline
Symbols & Description \\ \hline
$k$ & the number of data nodes in an array \\ \hline
$r$ & the number of local parity nodes in an array \\ \hline
$n$ & the number of nodes in an array ($n=k+r$) \\ \hline
$h$ & the number of arrays \\ \hline
$g$ & the number of global parity nodes \\ \hline
LP & local parity nodes \\ \hline
GP & global parity nodes \\ \hline
ID & important data \\ \hline
UD & unimportant data \\ \hline
\end{tabular}
\end{table}

@@

STAR code \cite{STAR} is an extension of the double-erasure-correcting EVENODD \cite{EVENODD} code, and a modification of the generalized triple-erasure-correcting EVENODD code. It employs a novice diagonal redundancy as shown in Figure \ref{fig:star-enc}.
\begin{figure}[!ht]
 \centering
 \subfigure[Horizontal parity coding (e.g., $C_{0,5} = C_{0,0} \oplus C_{0,1} \oplus C_{0,2} \oplus C_{0,3} \oplus C_{0,4}$).]{
  \includegraphics[width=0.20\textwidth]{photo/star-hori.pdf}
 }
 \hspace{5pt}
 \subfigure[Diagonal parity coding (e.g., $S_1 = C_{3,1} \oplus C_{2,2} \oplus C_{1,3} \oplus C_{0,4}$ and $C_{0,6} = C_{0,0} \oplus C_{3,2} \oplus C_{2,3} \oplus C_{1,4} \oplus S_1$).]{
  \includegraphics[width=0.20\textwidth]{photo/star-diag.pdf}
 } \\
 \subfigure[Anti-diagonal parity coding (e.g., $S_2 = C_{0,1} \oplus C_{1,2} \oplus C_{2,3} \oplus C_{3,4}$ and $C_{0,7} = C_{0,0} \oplus C_{1,1} \oplus C_{2,2} \oplus C_{3,3} \oplus S_2$).]{
  \includegraphics[width=0.20\textwidth]{photo/star-anti.pdf}
 }
 \hspace{5pt}
 \caption{Encoding of STAR code ($p = 5$).}
 \label{fig:star-enc}
\end{figure}

@@

\begin{table}[ht]
\centering 
\caption{Comparison of storage overhead, reliability and performance between EC, Approximate Storage and Approximate Code. (``Appr.'' is short for ``Approximate'')}\label{tab-AS-EC-AP}
\begin{tabular}{|c|c|c|c|c|}
\hline
\multicolumn{2}{|c|}{Schemes} & \begin{tabular}[c]{@{}c@{}}Storage\\ Overhead\end{tabular} & Reliability & Performance \\ \hline
\multirow{2}{*}{EC} & RS & high & high & medium \\ \cline{2-5} 
 & RAID-6 & medium & medium & high \\ \hline
\multicolumn{2}{|c|}{Appr. Storage} & low & low & high \\ \hline
\multirow{2}{*}{\begin{tabular}[c]{@{}c@{}}Appr.\\ Code\end{tabular}} & ID & \multirow{2}{*}{low} & high & high \\ \cline{2-2} \cline{4-5} 
 & UD &  & medium & high \\ \hline
\end{tabular}
\end{table}

@@

Since \emph{Structure I} distributes important data across each node, it guarantees a more balanced load. \emph{Structure II} concentrates important data into an array, and provides greater reliability for important data. A detailed analysis of this will be presented in \ref{evaluation}.

\subsubsection{Code Generation}
After code segmentation and structure selection, the Approximate Code Framework generates an approximate form of the input erasure code.

@@

\begin{figure}[ht]
\centering
\includegraphics[width=0.8\linewidth]{photo/AP-5214.pdf}
\caption{Construction of Approximate STAR Code (5,2,1,4,II)}
\label{fig-ap-5214}
\end{figure}

\begin{figure}[ht]
\includegraphics[width =0.8\linewidth]{photo/EVENODD-STAR-v2.pdf}
\caption{EVENODD only consist horizontal and diagonal parity, while STAR add the anti-diagonal parity node based on EVENODD and can tolerate 3 device failures.}\label{fig-star}
\end{figure}

@@

As introduced in \ref{existEC}, STAR Code \cite{huang2008star} has 3 parity chunks and it is a tipical 3DFTs XOR-based erasure code.
%We usually split the XOR-based code into a horizontal parity (local) and (anti-)diagonal parities (global), whereas the STAR feature allows it to support another segmentation method.
Since STAR is a direct extension of EVENODD\cite{blaum1995evenodd}, that is to say, the STAR that removes the anti-diagonal parity is the typical RAID-6 code EVENODD. As shown in Figure \ref{fig-star}, in this case, the horizontal and diagonal parity are used as local parities while the anti-diagonal parity is defined as global parity.
According to the construction requirements of STAR, each node is divided into 4 blocks.

Briefly, Approximate STAR Code (5,2,1,4,II) can be thought of as important data encoded by the full STAR, while unimportant data is encoded by a part of STAR, EVENODD. It is plain to see that important data can tolerate any 3 node failures while unimportant data can tolerate any 2 node failures.

\subsubsection{Approximate TIP Code}

optimal update complexity.

Figure \ref{fig-ap-TIP} is a tipical construction of Approximate Code ($5,1,6$) in \emph{Structure I}, based on RAID5 and TIP-code \cite{zhang2015tip}. RAID5 tolerate one node failure while TIP-code is an XOR-based 3DFTs code. In each array, local parity blocks provide horizontal XOR parity, and between arrays, global parity provide diagonal parity and anti-diagonal parity.

The local (horizontal) parity elements are calculated by the following encoding equations.
\begin{align}
    LP_{i,0} &= \bigoplus_{j=0}^{k-1} ID_{i,j} (0 \leqslant i < h)\\
    LP_{i,p}(0<p<s) &= \bigoplus_{j=k(p-1)}^{kp-1} UD_{i,j} (0 \leqslant i < h)
\end{align}

When generating global parity blocks, the important data block, the local parity block, and the global parity block should be arranged as the encoding form of TIP-code. Figure \ref{fig-TIP} shows the coding method of diagonal and anti-diagonal parity blocks.
Since the encoding process of important data blocks can be seen as RAID5 plus TIP-code, it is obvious that they achieve 3DFTs.

\begin{figure}[ht]
\centering
\includegraphics[width=0.3\textwidth]{photo/AP-516.pdf}
\caption{The XOR-based Approximate Code ($5,1,6$, \emph{Structure I}), constructed based on RAID5 and TIP-code.}
\label{fig-ap-TIP}
\end{figure}

\begin{figure}[ht]
\subfigure[]{
\begin{minipage}[t]{0.45\linewidth}
\centering
\includegraphics[width=0.8\linewidth]{photo/RAID5.pdf}        
\end{minipage}
}
\subfigure[]{
\begin{minipage}[t]{0.45\linewidth}
\centering
\includegraphics[width=0.8\linewidth]{photo/legend.pdf}        
\end{minipage}
}

\subfigure[]{
\begin{minipage}[t]{0.45\linewidth}
\centering
\includegraphics[width=\linewidth]{photo/TIP-di.pdf}        
\end{minipage}
}
\subfigure[]{
\begin{minipage}[t]{0.45\linewidth}
\centering
\includegraphics[width=\linewidth]{photo/TIP-an.pdf}        
\end{minipage}
}
\caption{Encoding pf TIP-code}
\label{fig-TIP}
\end{figure}

\iffalse
\subsection{Case Study}
This section describe the decoding methods in different cases of node failure based on \emph{Structure I} and \emph{Structure II}.

\subsubsection{Reconstruction cases in Structure 1}
Under \emph{Structure I}, important data and unimportant data are distributed in the same nodes, so they suffer the same risk of device failures. 
When $r$ or less nodes fail, all the data can be reconstructed by local parity.
When the number of failed nodes is over $r$ but no more than 3, the Approximate Code conduct approximate recovery, in which the important data are recovered by global parity nodes and the damaged video data will be processed by the video recovery and fuzzy algorithm.

\subsubsection{Reconstruction cases in Structure 2}
Under \emph{Structure II}, we consider important and unimportant data nodes separately.

For node level failure, the fault tolerance of \emph{Structure II} is exactly as \emph{Structure I},When it comes to node level failures, \emph{Structure II} can tolerate more unimportant data node failures than \emph{Structure I}. The parity chain of important data does not pass through the unimportant data, so the damage of these nodes does not affect the recovery of important data.

///////////////////////
Under the random probability model of nodes, the probability of failure of the Approximate Code under 4 node damage is
\begin{equation}
    P_{failure} = \frac{C_{k+3}^4}{C_{(k+r)h+3-r}^4}
\end{equation}
which is the 4 node failure situation in $k$ important data nodes and 3 important parity nodes. For example, the failure situation of Approximate Code ($4,1,4$, \emph{Structure II}) probability is 0.478\%.
\fi

@@

We analyze the nature of the Approximate Code from the following aspects, and the calculation method of the relevant indicators is given in Table \ref{tab-AS-RS-AP}.
\begin{itemize}
    \item Low Storage Overhead: Approximate Code reduces storage overhead by approximating storage strategies. This property is more pronounced for data with a smaller proportion of important data.
    \item Low Update Overhead: When one node is updated, Approximate Code only needs to write $r \times h$ local parity nodes and only $3-r$ global parity nodes, while tipical 3DFTs EC methods should write $3 \times h$ parity nodes.
    \item High reliability for important data. The Approximate Code guarantees 3DFTs for important data.
    \item Flexibility. The implementation of the Approximate Code can be based on RS, XOR or a mixture of the two.
\end{itemize}

\begin{table}[]
\centering 
\caption{Comparison of storage overhead and fault tolerance between Ap-Code (short for Approximate Code), RS and several XOR-based codes.}\label{tab-AS-RS-AP}
\begin{tabular}{|c|c|c|c|}
\hline
EC & \begin{tabular}[]{@{}c@{}}Storage\\ Overhead\end{tabular} & \begin{tabular}[]{@{}c@{}}Fault \\ Tolerance\end{tabular} & \begin{tabular}[]{@{}c@{}}Single Node\\Update Cost\end{tabular} \\ \hline
RS($k,q$) & $(k+q)/k$ & $q$ & q \\ \hline
EVENODD($k,2$) & $(k+2)/k$ & 2 & 2 \\ \hline
TIP-code/STAR($k,3$) & $(k+r)/k$ & 3 & 3 \\ \hline
\begin{tabular}[]{@{}c@{}}Ap-Code\\ ($k,r,h$)\end{tabular} & $\frac {(k+r)h+3-r}{k \times h}$ & r to 3 & $r+\frac{3-r}{h}$ \\ \hline
\end{tabular}
\end{table}

\subsection{Implementation}\label{Implementation}
\begin{figure}[htb]
\centering
\includegraphics[height = 5cm]{photo/implementation-V2.pdf}
\caption{Overview of Approximate Code implementation}
\label{fig-implementation}
\end{figure}

Compared with the traditional scheme that does not consider the meaning of the upper array data, the Approximate Code pays attention to the difference of the importance of the data, so an intermediate array between the upper array application and the underlying distributed storage system is necessary to preprocess the data. We call it the approximate storage array, which include 3 parts: data identification and allocation, encoding and decoding process of Approximate Code and the video fuzzification and recovery.

\subsubsection{Data Segmentation and Distribution module}
The data segmentation module splits the video file stream into multiple data segments and automatically discriminates the important data. A natural approach is to follow the GOP segmentation. According to the \ref{video storage}, the GOP of the encoded video starts with an I frame, and all the data in that GOP depends on it for decoding, so we define it as important data and divide the GOP into I frames (important part) and other data. (unimportant part).

The data distribution module distributes important data and unimportant data in different blocks and records the location. This location information is also defined as important data. This module is also responsible for analyzing the proportion of important data and unimportant data in the data stream to select the most appropriate coding parameter configuration to ensure fault tolerance and high storage efficiency of important data.

\subsubsection{Approximate Code module}
The Approximate Code module is responsible for encoding and decoding important and unimportant data and completely recovering the data within fault tolerance. For data that cannot be recovered, the Approximate Code module transmits it to the video recovery module for approximate recover videos.

Approximate Code module is also responsible for allocating blocks of data to ensure that blocks of each array are distributed to different nodes, while ensuring that global check blocks and data blocks are not on one node.

@@

\iffalse
\section{Approximate Recovery}\label{ap-recovery}
\begin{figure*}\label{fig-node-lost}
\subfigure{
    \includegraphics[width = 0.22\linewidth]{photo/experiment/Ap-recovery-4-disks.eps}
}
\subfigure{
    \includegraphics[width = 0.22\linewidth]{photo/experiment/Ap-recovery-5-disks.eps}
}
\subfigure{
    \includegraphics[width = 0.22\linewidth]{photo/experiment/Ap-recovery-6-disks.eps}
}
\subfigure{
    \includegraphics[width = 0.22\linewidth]{photo/experiment/Ap-recovery-8-disks.eps}
}
\caption{Comparison of the data retention  between approximate storage and common methods when node is unrecoverable.}\label{fig-node-lost}
\end{figure*}

In the approximate recovery mode, since unimportant data suffers unrecoverable loss, the recovery of damaged video files must be considered. Therefore, we evaluate the recovery of the video file in this section.

\subsection{Experimental Setup}
\subsubsection{Coding Algorithm} 
We evaluate the condition of the video of H.264 encoding [] under approximate recovery. Mainly because H.264 is an advanced video coding algorithm widely used at present, at the same time, the common advanced coding algorithms have similar coding processes.

\subsubsection{Data Set}
We choose 100 videos from xxx data set[]. All videos are stored in ``.mp4'' format at 1280*720 HD resolution.

\subsubsection{Metrics}
We use the number of frames saved as an indicator to evaluate the ability of the approximate storage and normal scheme to preserve data in the event of an unrecoverable node failure.

We define that when the I frame of the video is corrupted, the entire GOP is marked as unavailable (lost).

Since the approximation code stores the I frame as important data, the integrity of the I frame is always guaranteed in our scheme.

\subsubsection{Simulation}
We store the video files on a single disk according to the approximate storage scheme and the common scheme, while traversing the damage of all the disks, from 1 to n-1, and counting the number of damaged p-frames and b-frames. We use this to get the number of P and B frames that can be completely saved in the case of m out of n disks.

\subsection{Results}
The experimental results are shown in Figure \ref{fig-node-lost}, where $n$ is 4,5,6 and 8. In a 8-node array, when 2 nodes are unrecoverable, the approximate recovery method protects nearly 1/4 P or B frames, while the common method lost more than half of these frames. In addition, the approximate storage scheme can guarantee the number of frames of the video close to the theoretical limit.

\subsection{Analysis}
Our experiments prove that if data is stored indiscriminately, the loss of important data will seriously affect the security of all data, and our scheme will control the data loss near the theoretical limit, ensuring video recovery and fuzzification. feasibility.

\subsection{Frame Recovery ????}
\fi

\section{Evaluation}\label{evaluation}
In this section, we conduct a series of experiments to demonstrate the efficiency of Approximate Code in HDFS. 
\subsection{Evaluation Methodology }
We choose the RS code to compare with several XOR-based code, including TIP-code, EVENODD, STAR, RAID5 and RAID6. Since 3DFTs are typical configurations, we set the number of check nodes for the RS to 3.
Experiments as well as mathematical analysis are used to demonstrate the performance of Approximate Code.

@@

\subsubsection{Metrics and Methods for Experiments: }
We use \textbf{Encoding Time} and \textbf{Recovery Time} as the metrics in our experiments.

Our experiment includes the calculation of these two metrics and can mainly be divided into several cases.
We measure the encoding time by calculating the time to generate all parity blocks, and we measure the recovery time by calculating the time to fully or approximately recover the failure nodes.
Both of them should be divided into 3 situation: single, double and triple node, so we discuss them separately.
Also, the encoding and recovery time consist of computation time, I/O time and transimission time in distributed file system, which should be considered separately.

The environment of our experiments are shown in Table \ref{tab-platform}. We set a Hadoop system with one NameNode and 4 DataNodes. \textcolor{gray}{text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text }

\begin{table}[]
\begin{tabular}{|l|l|}
\hline
Description & DELL R730 Server \\ \hline
CPU & Intel Xeon 3.0GHz \\ \hline
NIC 1Gbps & 1Gbps \\ \hline
Memory & 32GB \\ \hline
Disk & 8TB HDD \\ \hline
OS & Linux 3.19 \\ \hline
Platform & Hadoop HDFS 3.0.3 \\ \hline
\end{tabular}
\caption{Details of Our Evaluation Platform}\label{tab-platform}
\end{table}

\subsection{Metrics and Methods of Experiment}
The metric of our experiments is time. The independent variable in this experiment is the number of nodes. We change the number of data nodes with different methods to compare the operation time. The experiments are divided into two parts, as one part is for measuring the encoding time of different methods, the other part is for timing the decoding time of different methods. The unit of the time is micro-second.\par

>>>>

To address this problem, in this paper, we propose Approximate Code, which is an erasure coding framework for video applications in cloud storage systems. The key idea of Approximate Code is distinguishing the important data and unimportant data in videos with different capabilities of fault tolerance. On one hand, for important data, Approximate Code provides triple parities to provide high reliability. On the other hand, single/double parities are applied for unimportant data, which can save the storage cost and accelerate the recovery process. To demonstrate the effectiveness of Approximate Code, we conduct several experiments in Hadoop systems. The results show that, compared to traditional 3DFTs using various erasure codes such as RS, STAR and TIP-Code, Approximate Code reduces the number of parities by up to 55\%, saves the storage cost by up to 20.8\%, increase the recovery speed by up to 1.25X when single disk fails, and can reconstruct the whole video data via fuzzification when triple disks fail.
\end{abstract}

@@

\section{Introduction}
For typical cloud storage systems such as Windows Azure \cite{calder2011windows} and Amazon AWS \cite{bermudez2013exploring}, erasure coding is a popular technique to provide both high reliability and low monetary cost \cite{EVENODD, RDP, BlaumRoth, XCode, CRS, TripleStar, TPtech, RSL}, where triple disk failure fault tolerant arrays (3DFTs) are widely used. Typical erasure codes can be divided into two categories, RS-based Codes \cite{RS} \cite{LRC} and XOR-based codes \cite{EVENODD, hcode, STAR, tip}. RS-based codes are encoded according the Galois Field Computation in Reed Solomon Code \cite{RS}, which allow flexible configuration and have a little higher computation cost. XOR-based codes simplify the computation, but the scalability is a significant issue in previous literatures.

@@

To address the above problem, in this paper, we propose Approximate Code\footnote{This article abbreviates ``Approximate'' to ``Appr. '' when necessary.}, which is an erasure coding framework to provide comprehensive solution for video data storage in cloud systems. The key idea of Approximate Code is treating the important/unimportant data in different ways. For important data, we add additional parities to provide high capability of fault tolerance. On the other hand, the unimportant data are encoded with a minimum number of parities, which only supply the basic requirement of the recovery. When triple disks fail, the lost data can be reconstructed via a fuzzy manner.

@@

\begin{table}[]
\caption{The symbols used in this paper.}\label{parameter}
\centering
\begin{tabular}{|c|l|}
\hline
Symbols & Description \\ \hline
$k$ & the number of data nodes in an array \\ \hline
$r$ & the number of local parity nodes in an array \\ \hline
$n$ & the number of nodes in an array ($n=k+r$) \\ \hline
$h$ & the number of arrays \\ \hline
$g$ & the number of global parity nodes \\ \hline
$E_{i,j}$ & element at the $i$-th row and $j$-th column \\ \hline 
LP & local parity nodes \\ \hline
GP & global parity nodes \\ \hline
ID & important data \\ \hline
UD & unimportant data \\ \hline
\end{tabular}
\end{table}

@@

STAR code \cite{STAR} is an extension of the double-erasure-correcting EVENODD \cite{EVENODD} code, and a modification of the generalized triple-erasure-correcting EVENODD code. It employs a novice diagonal redundancy as shown in Figure \ref{fig:star-enc}.
\begin{figure}[!ht]
 \centering
 \subfigure[Horizontal parity coding (e.g., $E_{0,5} = E_{0,0} \oplus E_{0,1} \oplus E_{0,2} \oplus E_{0,3} \oplus E_{0,4}$).]{
  \includegraphics[width=0.20\textwidth]{photo/star-hori.pdf}
 }
 \hspace{5pt}
 \subfigure[Diagonal parity coding (e.g., $S_1 = E_{3,1} \oplus E_{2,2} \oplus E_{1,3} \oplus E_{0,4}$ and $E_{0,6} = E_{0,0} \oplus E_{3,2} \oplus E_{2,3} \oplus E_{1,4} \oplus S_1$).]{
  \includegraphics[width=0.20\textwidth]{photo/star-diag.pdf}
 } \\
 \subfigure[Anti-diagonal parity coding (e.g., $S_2 = E_{0,1} \oplus E_{1,2} \oplus E_{2,3} \oplus E_{3,4}$ and $E_{0,7} = E_{0,0} \oplus E_{1,1} \oplus E_{2,2} \oplus E_{3,3} \oplus S_2$).]{
  \includegraphics[width=0.20\textwidth]{photo/star-anti.pdf}
 }
 \hspace{5pt}
 \caption{Encoding of STAR code ($p = 5$).}
 \label{fig:star-enc}
\end{figure}

@@

\begin{table}[ht]
\centering 
\caption{Comparison of storage overhead, reliability and performance between EC, Approximate Storage and Approximate Code.}\label{tab-AS-EC-AP}
\begin{tabular}{|c|c|c|c|c|}
\hline
\multicolumn{2}{|c|}{Schemes} & \begin{tabular}[c]{@{}c@{}}Storage\\ Overhead\end{tabular} & Reliability & Performance \\ \hline
\multirow{2}{*}{EC} & RS & high & high & medium \\ \cline{2-5} 
 & RAID-6 & medium & medium & high \\ \hline
\multicolumn{2}{|c|}{Appr.  Storage} & low & low & high \\ \hline
\multirow{2}{*}{\begin{tabular}[c]{@{}c@{}}Appr. \\ Code\end{tabular}} & ID & \multirow{2}{*}{low} & high & high \\ \cline{2-2} \cline{4-5} 
 & UD &  & medium & high \\ \hline
\end{tabular}
\end{table}

@@

Since \emph{Structure I} distributes important data across each node, it guarantees a more balanced load. \emph{Structure II} concentrates important data into an array, and provides greater reliability for important data. A detailed analysis of this will be presented in Section +\ref{ReconstructionFT}.

\subsubsection{Code Generation}\label{code-gen}
After code segmentation and structure selection, the Approximate Code Framework generates an approximate form of the input erasure code.

@@

\begin{figure}[ht]
\centering
\includegraphics[width=0.7\linewidth]{photo/AP-5214.pdf}
\caption{Construction of Approximate STAR Code (5,2,1,4,II)}
\label{fig-ap-5214}
\end{figure}

\begin{figure}[ht]
\includegraphics[width =0.8\linewidth]{photo/EVENODD-STAR-v2.pdf}
\caption{Encoding process of Approximate STAR Code (5,2,1,4,II), which can be divided into STAR (encode important data) and EVENODD (encode unimportant data).}\label{fig-star}
\end{figure}

@@

As introduced in \ref{existEC}, STAR Code \cite{STAR} has 3 parity chunks and it is a tipical 3DFTs XOR-based erasure code.
Since STAR is a direct extension of EVENODD\cite{EVENODD}, that is to say, the STAR that removes the anti-diagonal parity is the typical RAID-6 code EVENODD. As shown in Figure \ref{fig-star}, in this case, the horizontal and diagonal parity are used as local parities while the anti-diagonal parity is defined as global parity.
According to the construction requirements of STAR, each node is divided into 4 blocks.

Briefly, Approximate STAR Code (5,2,1,4,II) can be considered to be important data encoded by the full STAR, while the unimportant data is encoded by a portion of STAR, EVENODD. It is plain to see that important data can tolerate any 3 node failures while unimportant data can tolerate any 2 node failures.

\subsubsection{Approximate TIP Code}
We then intorduce the generation of Approximate TIP Code (5,1,2,6,I).

\begin{figure}[ht]
\centering
\includegraphics[width=0.3\textwidth]{photo/AP-5126.pdf}
\caption{Construction of Approximate TIP Code (5,1,2,6,I)}
\label{fig-ap-TIP}
\end{figure}

\begin{figure}[ht]
\centering
\includegraphics[width=0.8\linewidth]{photo/RAID5-TIP-v2.pdf}        
\caption{Encoding process of Approximate TIP Code (5,1,2,6,I), which can be divided into TIP (encode important data) and RAID-5 (encode unimportant data). (e.g., the diagonal parity block marked as a square $E_{4,5} = E_{4,0} \oplus E_{3,1} \oplus E_{2,2} \oplus E_{1,3} \oplus E_{0,4}$)}
\label{fig-TIP}
\end{figure}

The horizontal parity block of TIP code is defined as the local parity and the remaining two as the global parities.

As shown in Figure \ref{fig-ap-TIP}, 30 data nodes form 6 layers, where important data accounting for 1/6 of each node.
All data nodes generate 6 local parity nodes.
Important data blocks are rearranged to fit the parity form of TIP Code and generate two global parity nodes.
The encoding process of Approximate TIP Code (5,1,2,6,I) is shown in Figure \ref{fig-TIP}.

\subsection{Reconstruction Process and Fault Tolerance}\label{ReconstructionFT}
When $r$ or less nodes fail, all the data can be reconstructed by local parities.
When $r+g$ or less nodes fail, all the important data can be reconstructed by local and global parities.
However, in most cases, the loss of more nodes is also recoverable. We only consider two situations: $r+1$ and $r+g+1$. 
The former exceeds the fault tolerance of unimportant data, while the latter exceeds the fault tolerance of important data. As mentioned in \ref{code-gen}, $r+g$ is set to 3.
Approximate Codes based on different structures have different fault tolerance and reconstruction cases, so we discuss \emph{Structure I} and \emph{Structure II} respectively.

\subsubsection{Structure I}
Under \emph{Structure I}, important data and unimportant data are distributed in the same nodes, so they suffer the same risk of device failures.

For unimportant data, it is recoverable as long as the node loss per line does not exceed $r$. Therefore, the unrecoverable scenarios account for
$$\frac{kh}{\binom{(k+r)h+g}{r+1}}.$$
of all $r+1$ node failure cases. 
For important data, when 4 nodes fail, the unrecoverable scenarios account for
$$h*\frac{\sum_{i=0}^{g} {\binom{4-i}{k+r}*\binom{i}{g}} }{\binom{4}{(k+r)*h+g}}  (g=0,1)$$

In Approximate Code (3,1,2,3,I), 90.11\% 2-node failure is recoverable for unimportant data nodes and 95.50\% 4-node failure is recoverable for important data nodes.

\subsubsection{Structure II}
Important and unimportant data are storaged in different nodes under \emph{Structure II}.
When $r+1$ nodes fail, the unrecoverable scenarios for unimportant data account for
$$\frac{k(h-1)}{\binom{(k+r)h+g}{r+1}}.$$
When 4 nodes fail, the unrecoverable scenarios for important data account for
$$\frac{\binom{k+3}{4}}{\binom{(k+r)h+g}{4}}.$$
In Approximate Code (3,1,2,3,II), 93.41\% 2-node failure is recoverable for unimportant data nodes, and 98.50\% 4-node failure is recoverable for important data nodes.

@@

We analyze the nature of the Approximate Code from the following aspects, and the calculation method of the relevant indicators is given in Table \ref{tab-AS-RS-AP}.
\begin{itemize}
    \item Low Storage Overhead: Approximate Code reduces storage overhead by approximating and tiered storage strategies. This property is more pronounced for data with a smaller proportion of important data.
    \item Optimal Update Complexity: When one node is updated, Approximate RS Code only needs to write $r$ local parity nodes and only $g/h$ global parity nodes on average besides the write of data node.
    \item High reliability for important data. The Approximate Code guarantees 3DFTs for important data.
    \item Flexibility. The implementation of the Approximate Code can be based on RS, XOR or a mixture of the two.
\end{itemize}

\begin{table}[htb]
\centering 
\caption{Comparison of storage overhead, fault tolerance and average single write performance between RS, STAR, TIP, Approximate RS, Approximate STAR and Approximate TIP}\label{tab-AS-RS-AP}
\begin{tabular}{|c|c|c|c|}
\hline
EC & \begin{tabular}[c]{@{}c@{}}Storage\\ Overhead\end{tabular} & \begin{tabular}[c]{@{}c@{}}Fault\\ Tolerance\end{tabular} & \begin{tabular}[c]{@{}c@{}}Single Write\\ Performance(Average)\end{tabular} \\ \hline
RS($k,r$) & $(k+r)/k$ & $r$ & $r+1$ \\ \hline
STAR($k,3$) & $(k+3)/k$ & $3$ & $6-\frac{4}{k}$ \\ \hline
TIP-code($k,3$) & $(k+3)/k$ & $3$ & 4 \\ \hline
\begin{tabular}[c]{@{}c@{}}Appr. RS\\ ($k,r,g,h$)\end{tabular} & \multirow{3}{*}{$\frac{(k+r)h+g}{kh}$} & $r+g$ & $1+r+\frac{g}{h}$ \\ \cline{1-1} \cline{3-4} 
\begin{tabular}[c]{@{}c@{}}Appr. STAR\\ ($k,2,1,h$)\end{tabular} &  & 3 & $2\frac{k-h-1}{kh}+4$ \\ \cline{1-1} \cline{3-4} 
\begin{tabular}[c]{@{}c@{}}Appr. TIP\\ ($k,1,2,h$)\end{tabular} &  & 3 & $2+\frac{2}{h}$ \\ \hline
\end{tabular}
\end{table}

\subsection{Implementation}\label{Implementation}
\begin{figure}[htb]
\centering
\includegraphics[height = 5cm]{photo/implementation-V2.pdf}
\caption{Overview of Approximate Storage Layer}
\label{fig-implementation}
\end{figure}

Compared with the traditional scheme that does not consider the meaning of the upper layer data, the Approximate Code pays attention to the difference of the importance of the data, so an intermediate layer between the upper layer application and the underlying distributed storage system is necessary. We call it the approximate storage layer, which include 3 parts: data identification and allocation, encoding and decoding process of Approximate Code and the video fuzzification and recovery.

\subsubsection{Data Segmentation and Distribution module}
The data segmentation module splits the video file stream into multiple data segments and automatically discriminates the important data. A natural approach is to follow the GOP segmentation. According to the \ref{video storage}, the GOP of the encoded video starts with an I frame, and all the data in that GOP depends on it for decoding, so we define it as important data and divide the GOP into I frames (important part) and other data. (unimportant part).
%The data distribution module distributes important data and unimportant data in different blocks and records the location. This location information is also defined as important data. 
This module is also responsible for analyzing the proportion of important data and unimportant data in the data stream to select the most appropriate coding parameter configuration to ensure fault tolerance and high storage efficiency of important data.

\subsubsection{Approximate Code module}
The Approximate Code module is responsible for encoding and decoding important and unimportant data and completely recovering the data within fault tolerance. For data that cannot be recovered, the Approximate Code module transmits it to the video recovery module for approximate recover videos.
%Approximate Code module is also responsible for allocating blocks of data to ensure that blocks of each layer are distributed to different nodes, while ensuring that global check blocks and data blocks are not on one node.

@@

\section{Evaluation}\label{evaluation}
In this section, we conduct a series of experiments to demonstrate the efficiency of Approximate Code. 
\subsection{Evaluation Methodology }
To compared with Approximate Code, We choose several XOR-based code, including TIP-code, EVENODD, STAR, RAID5 and RAID6, RS code and LRC codes which are widely used in cloud storage systems. Since 3DFTs are typical configurations, we set the number of parity nodes to 3 for all kinds of codes in this evaluation.

Experiments as well as mathematical analysis are used to demonstrate the performance of Approximate Code.

@@

\subsubsection{Metrics and Methods for Experiments: }
We use \textbf{Encoding Time} and \textbf{Recovery Time} as the metrics in our experiments. \textbf{Encoding Time} is the time for generating all parity nodes and \textbf{Recovery Time} is the time for recovering the lost nodes.  Several codes are chosen to compared with Approximate Code with the same data nodes $k$. Attention that Approximate Code can only recover the important data nodes in some cases and we only keep the lost data nodes to be the same for all codes which means Approximate Code may recover less data than other codes.

The environment of our experiments are shown in Table \ref{tab-platform}. We set a Hadoop system with one NameNode and $h$ DataNodes. Each DataNodes storage the data of one layer of Approximate Code and the global parities are distributed at each DataNodes. We set $h=4,6$ and node size equal $1GB$ here as two common configurations.

Our experiment can mainly be divided into five cases. In the first part, we evaluate the encoding time for all kinds of codes. In the next three parts we measure the recovery time under single, double and triple failure nodes condition respectively. Finally we conduct the experiment of frame interpolation to prove that the lost of video frames is recoverable to some extent.

\begin{table}[!ht]
\begin{tabular}{|l|l|}
\hline
Description & DELL R730 Server \\ \hline
CPU & Intel Xeon 3.0GHz \\ \hline
NIC 1Gbps & 1Gbps \\ \hline
Memory & 32GB \\ \hline
Disk & 8TB HDD \\ \hline
OS & Linux 3.19 \\ \hline
Platform & Hadoop HDFS 3.0.3 \\ \hline
\end{tabular}
\caption{Details of Our Evaluation Platform}\label{tab-platform}
\end{table}

\subsection{Numerical Results of Mathematical Analysis}
\subsubsection{Storage Overhead}
We compare the storage overhead between RS (k,3), Appr. RS (k,1,2,h) and Appr. RS (k,2,1,h), where h = 4 or 6. As shown in Figure \ref{fig-Storage}, the results shows that Appr. RS Code has lower storage overhead than RS Code. The ratio of optimization is up to 21.4\% when h=4, k=4 and 23.8\% when h=6, k=4.

\subsubsection{Fault Tolerance}
All the erasure codes we evaluate in this Section are 3DFTs.
